BOLD Parameter Estimation Using Particle Filters

### 2010-09-03 doc/thesis/resultsB.tex
fixed one graph and added the pdf

\begin{figure}
\centering
\includegraphics[clip=truew,trim=8cm 4cm 8cm 4cm,width=16cm]{images/realhist}
\caption{Histogram of parameters in active regions (\acs{MI} $> .15$).}
\label{fig:realhist}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[clip=true,trim=6cm 1cm 5cm 1cm,width=\textwidth]{images/realhist}
\caption{Histogram of parameters in active regions (\acs{MI} $> .15$) overlayed
with the parameter estimates from Friston et al. \cite{Friston2002b}}
\label{fig:realhist}
\end{figure}
